Clean and Process Raw Data

### 2019-07-30 data-raw/README.Rmd
Update raw-data README

---
title: "Clean 2015 Raw Data"
output: github_document
---

@@

@@

```{r}

library(readr)
library(dplyr)

# Preprocess 2015 data for all assessment dates

files <-
  list.files("data", pattern = "^DS2015_Raw", full.names = TRUE)

@@

  x <- dplyr::arrange(x, REP, TRT)

@@

  # Calculate tiller sheath blight incidence -----------------------------------
  x <-
    x %>%
    dplyr::mutate(TShB_incidence = NTShB / NTIL)

  TShB_incidence <-
    x %>% dplyr::select(REP,
                        TRT,
                        WMGT,
                        NRTE,
                        SMPL,
                        HILL,
                        HGHT,
                        NTIL,
                        NTShB,
                        TShB_incidence)

@@

  for (i in 1:4) {
    y <-
      x %>%
      dplyr::select(
        TRT,
        REP,
        WMGT,
        SMPL,
        NRTE,
        HILL,
        paste0("TIL", i),
        paste0("GL", i),
        paste0("DL", i),
        paste0("SHB", i),
        paste0("SLA", i),
        paste0("SLB", i),
        paste0("SLC", i),
        paste0("SLD", i),
        paste0("SLE", i),
        paste0("SLF", i)
      ) %>%
      tidyr::gather(LEAF,
                    LEAF_ShB,
                    dplyr::starts_with("SL"))

@@

  z <- dplyr::bind_rows(TIL)
  x <- dplyr::left_join(TShB_incidence, z)

@@

# Run reformat function for all 2015 files -------------------------------------
DS2015 <- purrr::map_df(files, reformat)

@@

DS2015$YEAR <- lubridate::year(DS2015$DATE)

@@

# Arrange columns --------------------------------------------------------------
DS2015 <-
  DS2015 %>% dplyr::select(
    YEAR,
    DATE,
    ASMT,
    DAI,
    REP,
    PLOT,
    TRT,
    SMPL,
    HILL,
    TIL,
    LEAF,
    GL,
    DL,
    TShB_incidence,
    TIL_ShB,
    LEAF_ShB,
    WMGT,
    NRTE
  )

@@

DS2015 <- tibble::as_tibble(dplyr::arrange(DS2015, ASMT, PLOT))

@@

# First assessment -------------------------------------------------------------
DS2016_A1 <- readr::read_csv("data/DS2016_Raw_1.csv")
# Fill missing values in NTIL and NTShB
DS2016_A1 <-
  DS2016_A1 %>% tidyr::fill(NTIL)
DS2016_A1 <-
  DS2016_A1 %>% tidyr::fill(NTShB)

@@

# Second assessement -----------------------------------------------------------
DS2016_A2 <- readr::read_csv("data/DS2016_Raw_2.csv")
DS2016_A2 <-
  DS2016_A2 %>% tidyr::fill(NTIL)
DS2016_A2 <-
  DS2016_A2 %>% tidyr::fill(NTShB)

@@

# Third assessement ------------------------------------------------------------
DS2016_A3 <- readr::read_csv("data/DS2016_Raw_3.csv")
DS2016_A3 <-
  DS2016_A3 %>% tidyr::fill(NTIL)
DS2016_A3 <-
  DS2016_A3 %>% tidyr::fill(NTShB)

@@

# Fourth assessment ------------------------------------------------------------
DS2016_A4 <- readr::read_csv("data/DS2016_Raw_4.csv")
DS2016_A4 <-
  DS2016_A4 %>% tidyr::fill(NTIL)
DS2016_A4 <-
  DS2016_A4 %>% tidyr::fill(NTShB)

@@

DS2016 <-
  DS2016 %>%
  tidyr::gather(
    LEAF,
    LEAF_ShB,
    dplyr::starts_with("ShBL"),
    -DATE,
    -ASMT,
    -DAI,
    -PLOT,
    -TRT,
    -REP,
    -WMGT,
    -SMPL,
    -NRTE,
    -HILL,
    -NTIL,
    -GL,
    -DL,
    -NTShB,
    -NSHShB,
    -TIL
  )

@@

# calculate tiller sheath blight incidence
DS2016 <-
  DS2016 %>%
  dplyr::group_by(DATE, ASMT, DAI, REP, PLOT, TRT, WMGT, NRTE, SMPL, HILL) %>%
  dplyr::mutate(TShB_incidence = NTShB / NTIL)

DS2016 <- dplyr::rename(DS2016, TIL_ShB = NSHShB)

DS2016$YEAR <- lubridate::year(DS2016$DATE)
DS2016$LEAF_ShB <- as.numeric(DS2016$LEAF_ShB)

DS2016 <-
  DS2016 %>% dplyr::select(
    YEAR,
    DATE,
    ASMT,
    DAI,
    REP,
    PLOT,
    TRT,
    SMPL,
    HILL,
    TIL,
    LEAF,
    GL,
    DL,
    TShB_incidence,
    TIL_ShB,
    LEAF_ShB,
    WMGT,
    NRTE
  )

DS2016 <- tibble::as_tibble(dplyr::arrange(DS2016, ASMT, PLOT))

@@

DAYS_2016 <- lubridate::time_length(DATE_1 - DATE_2, unit = "day")
DS2016$DAYS <-
  c(rep(0, nrow(DS2016) - length(DAYS_2016)), DAYS_2016)

@@

# Arrange columns --------------------------------------------------------------
DS2016 <-
  DS2016 %>% dplyr::select(
    YEAR,
    DATE,
    ASMT,
    DAI,
    REP,
    PLOT,
    TRT,
    SMPL,
    HILL,
    TIL,
    LEAF,
    GL,
    DL,
    TShB_incidence,
    TIL_ShB,
    LEAF_ShB,
    WMGT,
    NRTE,
    DAYS
  )
```

# Calculating Area Under the Disease Progress Stairs (AUDPS)

Because the data were collected on an ordinal scale, but not evenly spaced,
the data are converted to the midpoint value of the percent range for severity
and then the AUDPS is calculated from that. See lines 544 and 559 for this.

After that the AUDPS is calculated using functionality from the _agricolae_
package.

@@

RAW_data <- tibble::as_tibble(rbind(as.data.frame(DS2015),
                                    as.data.frame(DS2016)))

@@

# reorder the treatments by level/year - low to high, 2015-2016 for graphs -----
RAW_data$NRTE <-
  forcats::fct_relevel(RAW_data$NRTE,
                       "0",
                       "100",
                       "120",
                       "60",
                       "180")

RAW_data$TRT <-
  forcats::fct_relevel(
    RAW_data$TRT,
    "AWD_N0",
    "AWD_N100",
    "AWD_N120",
    "AWD_N60",
    "AWD_N180",
    "PDL_N0",
    "PDL_N100",
    "PDL_N120",
    "PDL_N60",
    "PDL_N180"
  )

# add column with midpoint % tiller ShB severity -------------------------------
RAW_data <-
  dplyr::mutate(
    RAW_data,
    PERC_TIL_ShB = dplyr::case_when(
      TIL_ShB == 0 ~ 0,
      TIL_ShB == 1 ~ 1,
      TIL_ShB == 2 ~ 2.5,
      TIL_ShB == 3 ~ 10,
      TIL_ShB == 4 ~ 32.5,
      TRUE ~ 75
    )
  )

# add column with midpoint % leaf ShB severity ---------------------------------
RAW_data <-
  dplyr::mutate(
    RAW_data,
    PERC_LEAF_ShB = dplyr::case_when(
      LEAF_ShB == 0 ~ 0,
      LEAF_ShB == 1 ~ 1,
      LEAF_ShB == 2 ~ 2.5,
      LEAF_ShB == 3 ~ 10,
      LEAF_ShB == 4 ~ 32.5,
      TRUE ~ 75
    )
  )

DS2015 <- subset(RAW_data, YEAR == "2015")
DS2016 <- subset(RAW_data, YEAR == "2016")

# calculate AUDPS values -------------------------------------------------------

@@

# 2015 Tiller incidence setup --------------------------------------------------
TShB_inc_15 <-
  DS2015 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_incidence = TShB_incidence)) %>%
  dplyr::arrange(PLOT)

TShB_inc_wide <-
  reshape2::dcast(TShB_inc_15, PLOT ~ ASMT, value.var = "PLOT_TShB_incidence")

# 2015 Tiller Severity AUDPS ---------------------------------------------------
TShB_sev_15 <-
  DS2015 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_severity = TIL_ShB)) %>%
  dplyr::arrange(PLOT)

@@

TShB_perc_15 <-
  DS2015 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_PERCENT = PERC_TIL_ShB)) %>%
  dplyr::arrange(PLOT)

@@

# 2015 Leaf Severity setup -----------------------------------------------------
LShB_sev_15 <-
  DS2015 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_LShB_severity = LEAF_ShB)) %>%
  dplyr::arrange(PLOT)

@@

LShB_perc_15 <-
  DS2015 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_LShB_PERCENT = PERC_LEAF_ShB)) %>%
  dplyr::arrange(PLOT)

@@

TShB_inc_AUDPS <-
  agricolae::audps(evaluation = TShB_inc_wide[, 2:6],
                   dates = dplyr::pull(TShB_inc_15[1:5, 6]))

TShB_sev_AUDPS <-
  agricolae::audps(evaluation = TShB_sev_wide[, 2:6],
                   dates = dplyr::pull(TShB_sev_15[1:5, 6]))

LShB_sev_AUDPS <-
  agricolae::audps(evaluation = LShB_sev_wide[, 2:6],
                   dates = dplyr::pull(LShB_sev_15[1:5, 6]))

TShB_percent_AUDPS <-
  agricolae::audps(evaluation = TShB_perc_wide[, 2:6],
        dates = dplyr::pull(TShB_perc_15[1:5, 6]))

LShB_percent_AUDPS <-
  agricolae::audps(evaluation = LShB_perc_wide[, 2:6],
        dates = dplyr::pull(LShB_perc_15[1:5, 6]))

AUDPS_15 <-
  tibble::as_tibble(
    cbind(
      PLOT = 1:24,
      TShB_inc_AUDPS,
      TShB_sev_AUDPS,
      TShB_percent_AUDPS,
      LShB_sev_AUDPS,
      LShB_percent_AUDPS
    )
  )

@@

ShB_15 <- dplyr::left_join(TShB_inc_15, AUDPS_15, by = "PLOT")

@@

# 2016 Tiller Incidence setup --------------------------------------------------
TShB_inc_16 <-
  DS2016 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_incidence = TShB_incidence)) %>%
  dplyr::arrange(PLOT)

@@

TShB_sev_16 <-
  DS2016 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_severity = TIL_ShB)) %>%
  dplyr::arrange(PLOT)

@@

TShB_perc_16 <-
  DS2016 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_PERCENT = PERC_TIL_ShB)) %>%
  dplyr::arrange(PLOT)

@@

LShB_sev_16 <-
  DS2016 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_LShB_severity = LEAF_ShB)) %>%
  dplyr::arrange(PLOT)

@@

LShB_perc_16 <-
  DS2016 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_LShB_PERCENT = PERC_LEAF_ShB)) %>%
  dplyr::arrange(PLOT)

@@

TShB_inc_AUDPS <-
  agricolae::audps(evaluation = TShB_inc_wide[, 2:5],
                   dates = dplyr::pull(TShB_inc_16[1:4, 6]))

TShB_sev_AUDPS <-
  agricolae::audps(evaluation = TShB_sev_wide[, 2:5],
                   dates = dplyr::pull(TShB_sev_16[1:4, 6]))

LShB_sev_AUDPS <-
  agricolae::audps(evaluation = LShB_sev_wide[, 2:5],
                   dates = dplyr::pull(LShB_sev_16[1:4, 6]))

TShB_percent_AUDPS <-
  agricolae::audps(evaluation = TShB_perc_wide[, 2:5],
                   dates = dplyr::pull(TShB_perc_16[1:4, 6]))

LShB_percent_AUDPS <-
  agricolae::audps(evaluation = LShB_perc_wide[, 2:5],
                   dates = dplyr::pull(LShB_perc_16[1:4, 6]))

AUDPS_16 <-
  tibble::as_tibble(
    cbind(
      PLOT = 1:16,
      TShB_inc_AUDPS,
      TShB_sev_AUDPS,
      TShB_percent_AUDPS,
      LShB_sev_AUDPS,
      LShB_percent_AUDPS
    )
  )

@@

ShB_16 <- dplyr::left_join(TShB_inc_16, AUDPS_16, by = c("PLOT" = "PLOT"))

# Merge AUDPS data for graphing ------------------------------------------------
AUDPS <- tibble::as_data_frame(tibble::as_tibble(rbind(ShB_15, ShB_16)))
AUDPS <- tidyr::separate(data = AUDPS, col = TRT,
                         sep = "_",
                         into = c("WMGT", "NRTE"))
AUDPS <- dplyr::mutate_at(.tbl = AUDPS,
                              .funs = factor,
                              .vars = c("WMGT", "NRTE"))

# Arrange NRTE values
AUDPS$NRTE <-
  forcats::fct_relevel(AUDPS$NRTE,
                       "N0",
                       "N100",
                       "N120",
                       "N60",
                       "N180")

@@

usethis::use_data(RAW_data,
                  compress = "bzip2",
                  overwrite = TRUE)

usethis::use_data(AUDPS,
                  compress = "bzip2",
                  overwrite = TRUE)
```

@@

usethis::use_data(N_rates,
                  compress = "bzip2",
                  overwrite = TRUE)
```

>>>>

---
title: "Clean and Process Raw Data"
output:
  github_document:
    pandoc_args: --webtex
---

@@

# Load Libraries

```{r libraries}
library(tidyverse)
library(agricolae)
library(usethis)
```

@@

Preprocess 2015 data for all assessment dates

```{r 2015Exp}
files <-
  list.files("data", pattern = "^DS2015_Raw", full.names = TRUE)

@@

  x <- arrange(x, REP, TRT)

@@

  # Calculate tiller sheath blight incidence -----------------------------------
  x <-
    x %>%
    mutate(TShB_incidence = NTShB / NTIL)

  TShB_incidence <-
    x %>% select(REP,
                        TRT,
                        WMGT,
                        NRTE,
                        SMPL,
                        HILL,
                        HGHT,
                        NTIL,
                        NTShB,
                        TShB_incidence)

@@

  for (i in 1:4) {
    y <-
      x %>%
      select(
        TRT,
        REP,
        WMGT,
        SMPL,
        NRTE,
        HILL,
        paste0("TIL", i),
        paste0("GL", i),
        paste0("DL", i),
        paste0("SHB", i),
        paste0("SLA", i),
        paste0("SLB", i),
        paste0("SLC", i),
        paste0("SLD", i),
        paste0("SLE", i),
        paste0("SLF", i)
      ) %>%
      gather(LEAF,
                    LEAF_ShB,
                    starts_with("SL"))

@@

  z <- bind_rows(TIL)
  x <- left_join(TShB_incidence, z)

@@

# Run reformat function for all 2015 files -------------------------------------
DS2015 <- map_df(files, reformat)

@@

DS2015$YEAR <- year(DS2015$DATE)

@@

# Arrange columns --------------------------------------------------------------
DS2015 <-
  DS2015 %>% select(
    YEAR,
    DATE,
    ASMT,
    DAI,
    REP,
    PLOT,
    TRT,
    SMPL,
    HILL,
    TIL,
    LEAF,
    GL,
    DL,
    TShB_incidence,
    TIL_ShB,
    LEAF_ShB,
    WMGT,
    NRTE
  )

@@

DS2015 <- arrange(DS2015, ASMT, PLOT)

@@

# First assessment -------------------------------------------------------------
DS2016_A1 <- read_csv("data/DS2016_Raw_1.csv")
# Fill missing values in NTIL and NTShB
DS2016_A1 <-
  DS2016_A1 %>% fill(NTIL)
DS2016_A1 <-
  DS2016_A1 %>% fill(NTShB)

@@

# Second assessement -----------------------------------------------------------
DS2016_A2 <- read_csv("data/DS2016_Raw_2.csv")
DS2016_A2 <-
  DS2016_A2 %>% fill(NTIL)
DS2016_A2 <-
  DS2016_A2 %>% fill(NTShB)

@@

# Third assessement ------------------------------------------------------------
DS2016_A3 <- read_csv("data/DS2016_Raw_3.csv")
DS2016_A3 <-
  DS2016_A3 %>% fill(NTIL)
DS2016_A3 <-
  DS2016_A3 %>% fill(NTShB)

@@

# Fourth assessment ------------------------------------------------------------
DS2016_A4 <- read_csv("data/DS2016_Raw_4.csv")
DS2016_A4 <-
  DS2016_A4 %>% fill(NTIL)
DS2016_A4 <-
  DS2016_A4 %>% fill(NTShB)

@@

DS2016 <-
  DS2016 %>%
  gather(
    LEAF,
    LEAF_ShB,
    starts_with("ShBL"),
    -DATE,
    -ASMT,
    -DAI,
    -PLOT,
    -TRT,
    -REP,
    -WMGT,
    -SMPL,
    -NRTE,
    -HILL,
    -NTIL,
    -GL,
    -DL,
    -NTShB,
    -NSHShB,
    -TIL
  )

@@

# calculate tiller sheath blight incidence
DS2016 <-
  DS2016 %>%
  group_by(DATE, ASMT, DAI, REP, PLOT, TRT, WMGT, NRTE, SMPL, HILL) %>%
  mutate(TShB_incidence = NTShB / NTIL)

DS2016 <- rename(DS2016, TIL_ShB = NSHShB)

DS2016$YEAR <- year(DS2016$DATE)
DS2016$LEAF_ShB <- as.numeric(DS2016$LEAF_ShB)

DS2016 <-
  DS2016 %>% select(
    YEAR,
    DATE,
    ASMT,
    DAI,
    REP,
    PLOT,
    TRT,
    SMPL,
    HILL,
    TIL,
    LEAF,
    GL,
    DL,
    TShB_incidence,
    TIL_ShB,
    LEAF_ShB,
    WMGT,
    NRTE
  )

DS2016 <- as_tibble(arrange(DS2016, ASMT, PLOT))

@@

DAYS_2016 <- time_length(DATE_1 - DATE_2, unit = "day")
DS2016$DAYS <-
  c(rep(0, nrow(DS2016) - length(DAYS_2016)), DAYS_2016)

@@

# Arrange columns --------------------------------------------------------------
DS2016 <-
  DS2016 %>% select(
    YEAR,
    DATE,
    ASMT,
    DAI,
    REP,
    PLOT,
    TRT,
    SMPL,
    HILL,
    TIL,
    LEAF,
    GL,
    DL,
    TShB_incidence,
    TIL_ShB,
    LEAF_ShB,
    WMGT,
    NRTE,
    DAYS
  )
```

# Calculating Disease Severity Index and Area Under the Disease Progress Stairs (AUDPS)

Because the data were collected on an ordinal scale, but not evenly spaced,
the data are converted to the midpoint value of the percent range for disease
severity index and then the AUDPS is calculated from that.

@@

RAW_data <- as_tibble(rbind(as.data.frame(DS2015),
                                    as.data.frame(DS2016)))

@@

# reorder the treatments by level/year - low to high, 2015-2016 for graphs -----
RAW_data$NRTE <-
  fct_relevel(RAW_data$NRTE,
                       "0",
                       "100",
                       "120",
                       "60",
                       "180")

RAW_data$TRT <-
  fct_relevel(
    RAW_data$TRT,
    "AWD_N0",
    "AWD_N100",
    "AWD_N120",
    "AWD_N60",
    "AWD_N180",
    "PDL_N0",
    "PDL_N100",
    "PDL_N120",
    "PDL_N60",
    "PDL_N180"
  )

# add column with midpoint % tiller ShB severity -------------------------------
RAW_data <-
  mutate(
    RAW_data,
    PERC_TIL_ShB = case_when(
      TIL_ShB == 0 ~ 0,
      TIL_ShB == 1 ~ 1,
      TIL_ShB == 2 ~ 2.5,
      TIL_ShB == 3 ~ 10,
      TIL_ShB == 4 ~ 32.5,
      TRUE ~ 75
    )
  )

# add column with midpoint % leaf ShB severity ---------------------------------
RAW_data <-
  mutate(
    RAW_data,
    PERC_LEAF_ShB = case_when(
      LEAF_ShB == 0 ~ 0,
      LEAF_ShB == 1 ~ 1,
      LEAF_ShB == 2 ~ 2.5,
      LEAF_ShB == 3 ~ 10,
      LEAF_ShB == 4 ~ 32.5,
      TRUE ~ 75
    )
  )

# add column with midpoint +1  % leaf ShB severity -----------------------------
RAW_data <-
  mutate(
    RAW_data,
    PERC_LEAF_ShB = case_when(
      LEAF_ShB == 0 ~ 1,
      LEAF_ShB == 1 ~ 2.5,
      LEAF_ShB == 2 ~ 10,
      LEAF_ShB == 3 ~ 32.5,
      LEAF_ShB == 4 ~ 75,
      TRUE ~ 100
    )
  )

DS2015 <- subset(RAW_data, YEAR == "2015")
DS2016 <- subset(RAW_data, YEAR == "2016")
```

# Calculate disease index values
See K. S. Chiang et al. 2017

DSI<sub>Modified</sub> = Mid<sub><em>Q</em></sub> + <em>R</em>/Total Number of Observations * (Mid<sub><em>Q+1</em></sub> - Mid<sub><em>Q</em></sub>)

```{r DSI}
TShB_sev_15 <- 
  DS2015 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
                      .vars = vars(PLOT_TShB_severity = TIL_ShB)) %>%
  arrange(PLOT) %>% 
  mutate(DSI = PERC_TIL_ShB + ())
```

```{r AUDPS}
# calculate AUDPS values -------------------------------------------------------

@@

# 2015 Tiller incidence AUDPS --------------------------------------------------
TShb_inc_15 <-
  DS2015 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  summarise_at(
    .funs = funs(mean(., na.rm = TRUE)),
    .vars = vars(PLOT_TShB_incidence = TShB_incidence)
  ) %>%
  arrange(PLOT) %>%
  group_by(YEAR, REP, TRT, PLOT) %>%
  summarise(AUDPS = audps(PLOT_TShB_incidence, DAYS))

# 2015 Tiller Severity AUDPS ---------------------------------------------------
TShB_sev_15 <-
  DS2015 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
                      .vars = vars(PLOT_TShB_severity = TIL_ShB)) %>%
  arrange(PLOT)

@@

TShB_perc_15 <-
  DS2015 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
                      .vars = vars(PLOT_TShB_PERCENT = PERC_TIL_ShB)) %>%
  arrange(PLOT)

@@

# 2015 Leaf Severity setup -----------------------------------------------------
LShB_sev_15 <-
  DS2015 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
                      .vars = vars(PLOT_LShB_severity = LEAF_ShB)) %>%
  arrange(PLOT)

@@

LShB_perc_15 <-
  DS2015 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
                      .vars = vars(PLOT_LShB_PERCENT = PERC_LEAF_ShB)) %>%
  arrange(PLOT)

@@

TShB_inc_AUDPS <-
  audps(evaluation = TShB_inc_wide[, 2:6],
                   dates = pull(TShB_inc_15[1:5, 6]))

TShB_sev_AUDPS <-
  audps(evaluation = TShB_sev_wide[, 2:6],
                   dates = pull(TShB_sev_15[1:5, 6]))

LShB_sev_AUDPS <-
  audps(evaluation = LShB_sev_wide[, 2:6],
                   dates = pull(LShB_sev_15[1:5, 6]))

TShB_percent_AUDPS <-
  audps(evaluation = TShB_perc_wide[, 2:6],
        dates = pull(TShB_perc_15[1:5, 6]))

LShB_percent_AUDPS <-
  audps(evaluation = LShB_perc_wide[, 2:6],
        dates = pull(LShB_perc_15[1:5, 6]))

AUDPS_15 <-
  as_tibble(
    cbind(
      PLOT = 1:24,
      TShB_inc_AUDPS,
      TShB_sev_AUDPS,
      TShB_percent_AUDPS,
      LShB_sev_AUDPS,
      LShB_percent_AUDPS
    )
  )

@@

ShB_15 <- left_join(TShB_inc_15, AUDPS_15, by = "PLOT")

@@

# 2016 Tiller Incidence setup --------------------------------------------------
TShB_inc_16 <-
  DS2016 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
                      .vars = vars(PLOT_TShB_incidence = TShB_incidence)) %>%
  arrange(PLOT)

@@

TShB_sev_16 <-
  DS2016 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
                      .vars = vars(PLOT_TShB_severity = TIL_ShB)) %>%
  arrange(PLOT)

@@

TShB_perc_16 <-
  DS2016 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
                      .vars = vars(PLOT_TShB_PERCENT = PERC_TIL_ShB)) %>%
  arrange(PLOT)

@@

LShB_sev_16 <-
  DS2016 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
                      .vars = vars(PLOT_LShB_severity = LEAF_ShB)) %>%
  arrange(PLOT)

@@

LShB_perc_16 <-
  DS2016 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
                      .vars = vars(PLOT_LShB_PERCENT = PERC_LEAF_ShB)) %>%
  arrange(PLOT)

@@

TShB_inc_AUDPS <-
  audps(evaluation = TShB_inc_wide[, 2:5],
                   dates = pull(TShB_inc_16[1:4, 6]))

TShB_sev_AUDPS <-
  audps(evaluation = TShB_sev_wide[, 2:5],
                   dates = pull(TShB_sev_16[1:4, 6]))

LShB_sev_AUDPS <-
  audps(evaluation = LShB_sev_wide[, 2:5],
                   dates = pull(LShB_sev_16[1:4, 6]))

TShB_percent_AUDPS <-
  audps(evaluation = TShB_perc_wide[, 2:5],
                   dates = pull(TShB_perc_16[1:4, 6]))

LShB_percent_AUDPS <-
  audps(evaluation = LShB_perc_wide[, 2:5],
                   dates = pull(LShB_perc_16[1:4, 6]))

AUDPS_16 <-
  as_tibble(
    cbind(
      PLOT = 1:16,
      TShB_inc_AUDPS,
      TShB_sev_AUDPS,
      TShB_percent_AUDPS,
      LShB_sev_AUDPS,
      LShB_percent_AUDPS
    )
  )

@@

ShB_16 <- left_join(TShB_inc_16, AUDPS_16, by = c("PLOT" = "PLOT"))

# Merge AUDPS data for graphing ------------------------------------------------
AUDPS <- as_data_frame(as_tibble(rbind(ShB_15, ShB_16)))
AUDPS <- separate(data = AUDPS, col = TRT,
                         sep = "_",
                         into = c("WMGT", "NRTE"))
AUDPS <- mutate_at(.tbl = AUDPS,
                              .funs = factor,
                              .vars = c("WMGT", "NRTE"))

# Arrange NRTE values
AUDPS$NRTE <-
  fct_relevel(AUDPS$NRTE,
                       "N0",
                       "N100",
                       "N120",
                       "N60",
                       "N180")

@@

use_data(RAW_data,
                  compress = "bzip2",
                  overwrite = TRUE)

use_data(AUDPS,
                  compress = "bzip2",
                  overwrite = TRUE)
```

@@

use_data(N_rates,
                  compress = "bzip2",
                  overwrite = TRUE)
```
